The Default Mode Network is a Reinforcement Learning Agent!

### 2018-03-10 paper/paper.tex
did a huge pass to integrate 2nd round of reviews

\title{Dark Control:\\
       Towards a Unified Account of Default Mode Function\\
       by Markov Decision Processes}

@@

The present work adopts the perspective of
a human \textit{agent} faced with the choice of the next actions
and guided by outcomes
of really happened, hypothetically imagined, and
expected futures to optimize behavioral performance.
Formally, a particularly attractive framework
to describe, quantify, and predict intelligent systems, such as the brain,
is proposed to be the combination of control theory and
reinforcement learning (RL). 
An intelligent agent improves the interaction with the environment
by continuously updating its computation of value estimates and action predispositions
through integration of feedback outcomes.
That is, ``[agents], with their actions, modify the environment and in doing so partially determine their next stimuli, in particular stimuli that are necessary for triggering the next action''
\citep{pezzulo2011grounding}.
Agents with other behavioral policies therefore sample different
distributions of action-perception trajectories \citep{ghavamzadeh2015bayesian}.
Henceforth,
\textit{control} refers to the influence that an agent exerts when interacting
with the environment to reach preferred states.

@@

The environment is generally taken as \textit{stochastic},
that is, changing in random ways. In addition, the environment is only
\textit{partially observable} in the sense that only limited aspects of the environment's
state are accessible to the agent's sensory input
\citep{starkweather2017dopamine}.
We assume that volatility of the environment
is realistic in a computational model which sets out
to explain DMN functions of the human brain.
% XXX: the following passage is already in the introduction
% Indeed, it is known that the more the external world is predictable,
% the more mental activity becomes detached from the actual sensory inputs
% \citep{antrobus1966studies, pope1978regulation},
% the more stimulus-independent thoughts occur, and
% the higher the neural activity in the DMN.
% Conversely, the more the currently executed task is unknown and unpracticed,
% the lower the DMN activity
% \citep{filler1973daydreaming, teasdale1995stimulus}.
% %
% These ``offline'' processes may however contribute to
% optimizing control of the organism.
% Such a framework of DMN funtion based on reinforcement learning
% can naturally embed human behavior
% in the tension between exploitative action with immediate gains and
% explorative action with longer-term reward schedules
% \citep{dayan2008decision}.
We argue that a functional account of the DMN based on RL
can naturally embed human behavior
in the tension between exploitative action with immediate gains and
explorative action with longer-term reward outcomes
\citep{dayan2008decision}.
In short, DMN implication in a diversity of
particularly sophisticated human behaviors
can be parsimoniously explained as instantiating probabilistic
simulations of experience coupled with prediction error minimization
to calibrate action trajectories for
reward outcome maximization at different time-scales.
Such a purposeful optimization objective
may be subserved by a stochastic approximation
based on a brain implementation of MCMC sampling.

@@

\paragraph*{Why Markov Decision Processes?} One may wonder whether MDP models are applicable to something as complex as human behavior. For instance, financial trading is largely a manifestation of strategic decision-making of interacting human agents. According to how the market responds, the agent incurs gain or loss as environmental feedback of the executed financial actions. Recent research on automatizing market exchanges by algorithmic trading has successfully used MDPs as a framework for modeling these elaborate behavioral dynamics  ~\citep{brazdil2017,yang15,yang14,yang12,dempster2006,hult2010, abergel2017}.
%
MDPs have also been effective as a behavioral model in robotics \citep{ng2004,abbeel2004} and in challenging multistep strategy games ~\citep{mnih2015,silver2016mastering,pritzel2017neural}.
%
As such, we aim to expand MDP applications as a useful model from "online" decision-making to the realms of "offline" behaviors most associated with the DMN.

@@

\paragraph*{Towards model-free reinforcement learning for the DMN.}
Model-free RL can be plausibly realized in the human brain \citep{doherty2015structure, daw2014algorithmic}.
Indeed,
it has been proposed \citep{gershman2015computational} that a core property of human intelligence is the improvement
of expected utility outcomes as a strategy for action choice in uncertain
environments, a situation perfectly captured by the formalism of MDPs.
It has also long been proposed \citep{dayan2008decision} that there
can be a direct mapping between model-free RL learning algorithms
and aspects of the brain.
The neurotransmitter dopamine could serve
as a 'teaching signal' to better estimate value associations
and action policies by controlling
synaptic plasticity in the reward-processing circuitry, including the NAc.
In contrast, \textit{model-based RL} would start off with some mechanistic assumptions about the dynamics of the world.
These can be assumptions about the physical laws governing the agent's environment or constraints on the state space, transition probabilities between states,
reward contingencies, etc.
% For instance, if a rat in a maze knows
% that standing still will produce no change in the environment, and in particular will not eventually lead to finding the food.
An agent might represent such knowledge about the world as follows:
\begin{itemize}
\item $r(s, \text{``stand still''}) = 0$ if $s$ does not correspond to a location
offering relevant resources.
\item $p(s'|s,\text{``stand still''}) = 1$ if $s'=s$ and $0$ otherwise.
\item etc.
\end{itemize}
% Model-based assumes knowledge of the environment in terms of the transition probabilities between states, the reward contingencies for state-action pairs, or any form of representation of the environment.
Such knowledge can be partly extracted from the environment: the agent infers a model of the world while learning to take optimal decisions based on the current representation of the environment. These methods learn what the effect is going to be of taking a particular action in a particular state. The result is an estimate of the underlying MDP which can then be either solved exactly or approximately, depending on the setting and what is feasible.

In contrast, model-free methods require no prespecified knowledge of the environment (transition probabilities, types of sensory input, etc.) or representation thereof. The agent infers which state-action pairs lead to reward through sampling the world in a trial-and-error manner and derives longer-term reward aggregates using environmental feedback information as an incentive. In so doing, model-free agents ultimately learn both an action policy and an implicit representations of the world. This distinction between model-free and model-based RL is similar to previous views \citep{dayan2014}.

@@

\subsubsection{Does the hippocampus subserve MCMC sampling?}
In RL, MCMC simulation is a common means to update the agent's belief state
based on stochastic sampling around states and possible transitions \citep{daw2014algorithmic}.
% \citep{silver2010monte}.
MCMC simulation provides a simple method for evaluating the value of a state.
This inference procedure provides an effective mechanism both for tree search (of the considered
action trajectories)
and for belief state updates, breaking the curse of dimensionality and allowing much greater scalability than an RL agent without stochastic resampling procedures.
Such methods have scaling as a function of available data (i.e., sample complexity) that
is determined only by the underlying difficulty of the MDP, rather than the size of the state space or observation space,
which can be prohibitively large.

In the human brain,
the HC could contribute to synthesizing imagined sequences of world states,
actions and rewards \citep{aronov2017, chao2017interaction, boyer2008evolutionary}.
These simulations of experience batches
would be used to update the value function, without ever looking inside the black box describing the model's dynamics.
A brain-imaging experiment in humans for instance identified hippocampal signals that specifically preceded upcoming choice performance in prospective planning in new environments
\citep{kaplan2017neural}.
This would be a simple control algorithm by evaluating all legal actions and selecting the action with
highest expected cumulative rewards.
In MDPs, MCMC simulation provides an effective mechanism both for tree search and for belief-based state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible \citep{silver2016mastering}.
This is because expected consequences of action choices can be well evaluated although only a subset of the states are actually considered \citep{daw2014algorithmic}.
% Much recent work points to MCMC or stochastic sampling-based approximations as a unifying framework for understanding how Bayesian inference may work practically across all these levels, in minds, brains, and machines. \textbf{XXX elvis: refs needed in last sentence. Plus, should be really bring up Bayesian?}

\paragraph*{A note on implicit and explicit memory.}
While Markov processes are usually memoryless, it is mathematically feasible to incorporate the previous states of such model into the current state. This extension may partially account for implicit memory at the behavioral level, but may not explain the underlying neurobiological implementation or accommodate explicit memory. Implicit memory-based processing arises in our MDP account of DMN function in several different forms: successive updates of a) the action policy and the value function, both being products of the past, as well as b) the deep non-linear relationships within the hierarchical connections of biological neural networks. The brain's adaptive synaptic connections can be thought as a deep neural-network architecture affording an implicit form of information compression of life experience. Such memory traces are stored in the neural machinery and can be implicitly retrieved as a form of knowledge during simulation of action rather than accessed as a stored explicit representation \citep{pezzulo2011grounding}. c) Certain neural processes in the hippocampus can be seen as some type of MCMC sampling for memory recall, which can also be a basis for probabilistic simulations across time-scales \citep{schacter2007remembering,Axelrod2017}.

@@

In comparison,
both the semantic hypothesis and the present formal account based on MDPs
expose mechanisms of how action considerations could be explored.
In both accounts,
there is also little reason to assume that contemplating alternative realities of various
levels of complexity, abstraction, time-scale, and purpose
rely on mechanisms that are qualitatively different. This interpretation concurs with
DMN activity increases across time, space, and content domains
demonstrated in many brain-imaging studies
\citep{spreng2009common, laird2009, bzdok2012morality, binder2009}.
Further, the semantic hypothesis
and MDP account offer explanations why HC damage does
not only impair recalling past events, but also imagining hypothetical and future
scenarios \citep{hassabis2007patients}.
While both semantic hypothesis and
our formal account propose memory-enabled, internally
generated information for probabilistic representation of action outcomes,
MDPs render explicit the grounds on which an action is
eventually chosen, namely, the estimated cumulative reward.
In contrast to many versions of the semantic hypothesis,
the MDPs naturally integrate the egocentric view
(more related to current action, state, and reward) and the
world view (more related to past and future actions, states, and rewards)
on the world in a same optimization problem.
Finally,
the semantic account of DMN function does not provide
suffcient explanation of \textit{how}
explicit world knowledge and logical analogies thereof
lead to foresight of future actions and states.
The semantic hypothesis does also not fully explain why memory recall
for scene construction in humans is typically fragmentary and noisy
instead of accurate and reliable.
In contrast to existing accounts on semantics and
mental scene construction, the random and creative aspects of DMN function
are explained in MDPs by the advantages of stochastic optimization.
Our MDP account provides an algorithmic explanation in that
stochasticity of the parameter space exploration
by MCMC approximation achieves better fine-tuning of the
action policies and inference of expected reward outcomes.
That is, the purposeful stochasticity of policy and value updates
in MDPs provides a candidate explanation for why humans
have evolved imperfect noisy memories
as the more advantageous adaptation.
In sum, mental scene construction according to the semantic
account is lacking an explicit time and incentive model,
both of which are integral parts of the MDP interpretation of DMN function.

@@

The difference between the FEP and the MDP account may be further clarified by a thought experiment.
Since theories based on the FEP \citep{friston2010free,fristonAIorRL}
conceptualize ongoing behavior
in an organism to be geared towards the surprise-minimizing goal,
an organism entering a dark room
% \footnote{\textit{Dark} is used here as an allegory to indicate the complete absence of any \textit{external} sensory input.}
(Fig. \ref{fig:darkroom}) would remain trapped in this location
because its sensory inputs are perfectly predictable
given the environmental state \citep{darkroom2012}.
\begin{wrapfigure}{r}{.37\linewidth}
  \centering
  \includegraphics[width=1.\linewidth]{darkroom_resized.png}
  \caption{\textbf{The dark room experiment.} An intelligent agent situated
  in a light-deprived closed space is used
  as a thought experiment for the complete absence
  of external sensory input.
  % The free-energy principle theory paradoxally predicts that such an agent would remain quietly in this room, such it perfectly predict all sensory input from such an environment.
  % However such behavior is not observed in humans or any animals: the agent would strive to leave such an environment in search of more ``interesting'' worlds.
  }
  \label{fig:darkroom}
\end{wrapfigure}
However, such a behavior is seldom observed in humans in the
real world. In a dark room, the intelligent agents would search for light sources by explore
the surroundings or aim to exit the room.
Defenders of the FEP have retorted by advancing the ``full package'' \citep{darkroom2012}:
FEP is proposed to be multi-scale and there would be a meta-scale at which the organism would
be \textit{surprised} by such a \textit{lack of surprise}. According to this argument, a dark room would paradoxically correspond to a state of particularly high relevance.
Driven by the surprise-minimization objective, the FEP agent would eventually bootstrap itself out of such saddle points to explore more interesting parts of the environment.
% Recourse to this argument is equivalent to invoking a \textit{halting oracle}\citep{haltingoracle}, an arbitrarily powerful machine which can solve the \textit{halting problem} (an arbitrarily difficult computational problem which cannot be solved under any reasonable \textit{model of computation}, not even in principle!). But this is problematic as it sucks up the problem (that of decision-making and active agency) the theory intends to elude in the first place.
In contrast, an organism operating under our RL-based theory would inevitably
identify the sensory-stimulus-deprived room as a local minimum. Indeed, hippocampal experience replay (see \ref{sec:self}) could serve to sample memories or fantasies of alternative situations
with reward structure. Such artificially generated \textit{internal} sensory input
subserved by the DMN can entice the organism to explore the room,
for instance by looking for and using the light switch or finding the room exit.

>>>>

% \title{Dark Control:\\
%        Towards a Unified Account of Default Mode Function\\
%        by Markov Decision Processes}
\title{The Default Mode Network is a Reinforcement Learning Agent!}

@@

The present work adopts the perspective of
a human \textit{agent} faced with the choice of the next actions
and guided by outcomes
of really happened, hypothetically imagined, and
expected futures to optimize behavioral performance.
Formally, we propose reinforcement learning to be a particularly attractive framework
to describe, quantify, DMN function and the brain.
An intelligent agent improves the interaction with the environment
by continuously updating its computation of value estimates and action predispositions
through integration of feedback outcomes.
That is, ``[agents], with their actions, modify the environment and in doing so partially determine their next stimuli, in particular stimuli that are necessary for triggering the next action''
\citep{pezzulo2011grounding}.
Agents with other behavioral policies therefore sample different
distributions of action-perception trajectories \citep{ghavamzadeh2015bayesian}.
Henceforth,
\textit{control} refers to the influence that an agent exerts when interacting
with the environment to reach preferred states.

@@

The environment is generally taken as \textit{stochastic},
that is, changing in random ways. In addition, the environment is only
\textit{partially observable} in the sense that only limited aspects of the environment's
state are accessible to the agent's sensory input
\citep{starkweather2017dopamine}.
We assume that volatility of the environment
is realistic in a computational model which sets out
to explain DMN functions of the human brain.
% XXX: the following passage is already in the introduction
% Indeed, it is known that the more the external world is predictable,
% the more mental activity becomes detached from the actual sensory inputs
% \citep{antrobus1966studies, pope1978regulation},
% the more stimulus-independent thoughts occur, and
% the higher the neural activity in the DMN.
% Conversely, the more the currently executed task is unknown and unpracticed,
% the lower the DMN activity
% \citep{filler1973daydreaming, teasdale1995stimulus}.
% %
% These ``offline'' processes may however contribute to
% optimizing control of the organism.
% Such a framework of DMN funtion based on reinforcement learning
% can naturally embed human behavior
% in the tension between exploitative action with immediate gains and
% explorative action with longer-term reward schedules
% \citep{dayan2008decision}.
We argue that a functional account of the DMN based on RL
can naturally embed human behavior
in the tension between exploitative action with immediate gains and
explorative action with longer-term reward outcomes
\citep{dayan2008decision}.
In short, DMN implication in a diversity of
particularly sophisticated human behaviors
can be parsimoniously explained as instantiating probabilistic
simulations of experience coupled with prediction error minimization
to calibrate action trajectories for
reward outcome maximization at different time-scales.
Such a purposeful optimization objective
may be subserved by a stochastic approximation
based on a brain implementation of Monte Carlo sampling.

@@

\paragraph*{Why Markov Decision Processes?} One may wonder whether MDP models
are applicable to something as complex as human behavior. The success of such
models in diverse domains are numerous. For instance, financial trading is largely a manifestation of strategic decision-making of interacting human agents. According to how the market responds, the agent incurs gain or loss as environmental feedback of the executed financial actions. Recent research on automatizing market exchanges by algorithmic trading has successfully used MDPs as a framework for modeling these elaborate behavioral dynamics  ~\citep{brazdil2017,yang15,yang14,yang12,dempster2006,hult2010, abergel2017}.
%
MDPs have also been effective as a behavioral model in robotics
\citep{ng2004,abbeel2004} and in challenging multistep strategy games
~\citep{mnih2015,silver2016mastering,pritzel2017neural}. An even recent work~\citep{robinowitz2018}
develops an MDP-based Theory of Mind for learning agents (the \textit{ToM-Net}).
The idea is to use-meta learning (learning-to-learn) to build strong priors
about the behavior of of a population of other agents.

% As such, we aim to expand MDP applications as a useful model from "online" decision-making to the realms of "offline" behaviors most associated with the DMN.

@@

\paragraph*{Reinforcement learning in the brain.}
Model-free RL can be plausibly realized in the human brain \citep{doherty2015structure, daw2014algorithmic}.
Indeed,
it has been proposed \citep{gershman2015computational} that a core property of human intelligence is the improvement
of expected utility outcomes as a strategy for action choice in uncertain
environments, a situation perfectly captured by the formalism of MDPs.
It has also long been proposed \citep{dayan2008decision} that there
can be a direct mapping between model-free RL learning algorithms
and aspects of the brain.
The neurotransmitter dopamine could serve
as a 'teaching signal' to better estimate value associations
and action policies by controlling
synaptic plasticity in the reward-processing circuitry, including the NAc.
In contrast, \textit{model-based RL} would start off with some mechanistic assumptions about the dynamics of the world.
These can be assumptions about the physical laws governing the agent's environment or constraints on the state space, transition probabilities between states,
reward contingencies, etc.
% For instance, if a rat in a maze knows
% that standing still will produce no change in the environment, and in particular will not eventually lead to finding the food.
An agent might represent such knowledge about the world as follows:
\begin{itemize}
\item $r(s, \text{``stand still''}) = 0$ if $s$ does not correspond to a location
offering relevant resources.
\item $p(s'|s,\text{``stand still''}) = 1$ if $s'=s$ and $0$ otherwise.
\item etc.
\end{itemize}
% Model-based assumes knowledge of the environment in terms of the transition probabilities between states, the reward contingencies for state-action pairs, or any form of representation of the environment.
Such knowledge can be partly extracted from the environment: the agent infers a model of the world while learning to take optimal decisions based on the current representation of the environment. These methods learn what the effect is going to be of taking a particular action in a particular state. The result is an estimate of the underlying MDP which can then be either solved exactly or approximately, depending on the setting and what is feasible.

% In contrast, model-free methods require no pre-specified knowledge of the environment (transition probabilities, types of sensory input, etc.) or representation thereof. The agent infers which state-action pairs lead to reward through sampling the world in a trial-and-error manner and derives longer-term reward aggregates using environmental feedback information as an incentive. In so doing, model-free agents ultimately learn both an action policy and an implicit representations of the world. This distinction between model-free and model-based RL is similar to previous views \citep{dayan2014}.

@@

\subsubsection{Does the hippocampus subserve Monte Carlo sampling?}
In RL, Monte Carlo simulation is a common means to update the agent's belief state
based on stochastic sampling around states and possible transitions \citep{daw2014algorithmic,silver2010monte}.
Monte Carlo simulation provides a simple method for evaluating the value of a state.
This inference procedure provides an effective mechanism both for tree search (of the considered
action trajectories)
and for belief state updates, breaking the curse of dimensionality and allowing much greater scalability than an RL agent without stochastic resampling procedures.
Such methods have scaling as a function of available data (i.e., sample complexity) that
is determined only by the underlying difficulty of the MDP, rather than the size of the state space or observation space,
which can be prohibitively large.

In the human brain,
the HC could contribute to synthesizing imagined sequences of world states,
actions and rewards \citep{aronov2017, chao2017interaction, boyer2008evolutionary}.
These simulations of experience batches
would be used to update the value function, without ever looking inside the black box describing the model's dynamics.
A brain-imaging experiment in humans for instance identified hippocampal signals that specifically preceded upcoming choice performance in prospective planning in new environments
\citep{kaplan2017neural}.
This would be a simple control algorithm by evaluating all legal actions and selecting the action with
highest expected cumulative rewards.
In MDPs, MC simulation provides an effective mechanism both for tree search and for belief-based state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible \citep{silver2016mastering}.
This is because expected consequences of action choices can be well evaluated although only a subset of the states are actually considered \citep{daw2014algorithmic}.
% Much recent work points to MCMC or stochastic sampling-based approximations as a unifying framework for understanding how Bayesian inference may work practically across all these levels, in minds, brains, and machines. \textbf{XXX elvis: refs needed in last sentence. Plus, should be really bring up Bayesian?}

\paragraph*{A note on implicit and explicit memory.}
While Markov processes are usually memoryless, it is mathematically feasible to
incorporate the previous states of such model into the current state. This
extension may partially account for implicit memory at the behavioral level, but
may not explain the underlying neurobiological implementation or accommodate
explicit memory. Implicit memory-based processing arises in our MDP account of
DMN function in several different forms: successive updates of a) the action
policy and the value function, both being products of the past, as well as b)
the deep non-linear relationships within the hierarchical connections of
biological neural networks. The brain's adaptive synaptic connections can be
thought as a deep neural-network architecture affording an implicit form of
information compression of life experience. Such memory traces are stored in the
neural machinery and can be implicitly retrieved as a form of knowledge during
simulation of action rather than accessed as a stored explicit representation
\citep{pezzulo2011grounding}. c) Certain neural processes in the hippocampus can
be seen as some type of Monte Carlo sampling for memory recall, which can also
be a basis for probabilistic simulations across time-scales
\citep{schacter2007remembering,Axelrod2017}.

@@

In comparison,
both the semantic hypothesis and the present formal account based on MDPs
expose mechanisms of how action considerations could be explored.
In both accounts,
there is also little reason to assume that contemplating alternative realities of various
levels of complexity, abstraction, time-scale, and purpose
rely on mechanisms that are qualitatively different. This interpretation concurs with
DMN activity increases across time, space, and content domains
demonstrated in many brain-imaging studies
\citep{spreng2009common, laird2009, bzdok2012morality, binder2009}.
Further, the semantic hypothesis
and MDP account offer explanations why HC damage does
not only impair recalling past events, but also imagining hypothetical and future
scenarios \citep{hassabis2007patients}.
While both semantic hypothesis and
our formal account propose memory-enabled, internally
generated information for probabilistic representation of action outcomes,
MDPs render explicit the grounds on which an action is
eventually chosen, namely, the estimated cumulative reward.
In contrast to many versions of the semantic hypothesis,
the MDPs naturally integrate the egocentric view
(more related to current action, state, and reward) and the
world view (more related to past and future actions, states, and rewards)
on the world in a same optimization problem.
Finally,
the semantic account of DMN function does not provide
suffcient explanation of \textit{how}
explicit world knowledge and logical analogies thereof
lead to foresight of future actions and states.
The semantic hypothesis does also not fully explain why memory recall
for scene construction in humans is typically fragmentary and noisy
instead of accurate and reliable.
In contrast to existing accounts on semantics and
mental scene construction, the random and creative aspects of DMN function
are explained in MDPs by the advantages of stochastic optimization.
Our MDP account provides an algorithmic explanation in that
stochasticity of the parameter space exploration
by Monte Carlo approximation achieves better fine-tuning of the
action policies and inference of expected reward outcomes.
That is, the purposeful stochasticity of policy and value updates
in MDPs provides a candidate explanation for why humans
have evolved imperfect noisy memories
as the more advantageous adaptation.
In sum, mental scene construction according to the semantic
account is lacking an explicit time and incentive model,
both of which are integral parts of the MDP interpretation of DMN function.

@@

The difference between the FEP and the MDP account may be further clarified by a thought experiment.
Since theories based on the FEP \citep{friston2010free,fristonAIorRL}
conceptualize ongoing behavior
in an organism to be geared towards the surprise-minimizing goal,
an organism entering a dark room
% \footnote{\textit{Dark} is used here as an allegory to indicate the complete absence of any \textit{external} sensory input.}

% (Fig. \ref{fig:darkroom})

would remain trapped in this location
because its sensory inputs are perfectly predictable
given the environmental state \citep{darkroom2012}.
% \begin{wrapfigure}{r}{.37\linewidth}
%   \centering
%   \includegraphics[width=1.\linewidth]{darkroom_resized.png}
%   \caption{\textbf{The dark room experiment.} An intelligent agent situated
%   in a light-deprived closed space is used
%   as a thought experiment for the complete absence
%   of external sensory input.
%   % The free-energy principle theory paradoxally predicts that such an agent would remain quietly in this room, such it perfectly predict all sensory input from such an environment.
%   % However such behavior is not observed in humans or any animals: the agent would strive to leave such an environment in search of more ``interesting'' worlds.
%   }
%   \label{fig:darkroom}
% \end{wrapfigure}
However, such a behavior is seldom observed in humans in the
real world. In a dark room, the intelligent agents would search for light sources by explore
the surroundings or aim to exit the room.
Defenders of the FEP have retorted by advancing the ``full package'' \citep{darkroom2012}:
FEP is proposed to be multi-scale and there would be a meta-scale at which the organism would
be \textit{surprised} by such a \textit{lack of surprise}. According to this argument, a dark room would paradoxically correspond to a state of particularly high relevance.
Driven by the surprise-minimization objective, the FEP agent would eventually bootstrap itself out of such saddle points to explore more interesting parts of the environment.
% Recourse to this argument is equivalent to invoking a \textit{halting oracle}\citep{haltingoracle}, an arbitrarily powerful machine which can solve the \textit{halting problem} (an arbitrarily difficult computational problem which cannot be solved under any reasonable \textit{model of computation}, not even in principle!). But this is problematic as it sucks up the problem (that of decision-making and active agency) the theory intends to elude in the first place.
In contrast, an organism operating under our RL-based theory would inevitably
identify the sensory-stimulus-deprived room as a local minimum. Indeed, hippocampal experience replay (see \ref{sec:self}) could serve to sample memories or fantasies of alternative situations
with reward structure. Such artificially generated \textit{internal} sensory input
subserved by the DMN can entice the organism to explore the room,
for instance by looking for and using the light switch or finding the room exit.
